\begin{longtable}{|p{12cm}|p{1.5cm}|}
\caption{Questionnaire: user roles}\\
\hline
\textbf{Which of the following roles apply to you?} & \textbf{Answers}\\
\hline
\endfirsthead
\multicolumn{2}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\textbf{Which of the following roles apply to you?} & \textbf{Answer} \\
\hline
\endhead
\hline \multicolumn{2}{c}{\textit{Continues on next page}} \\
\endfoot
\hline
\endlastfoot
I want to use the software only while working at the Systems Biology lab. & 3 \\ \hline
I am looking to use the software outside of the Systems Biology lab. & 3 \\
\end{longtable}


\begin{longtable}{|p{10cm}|p{0,5cm}|p{0,5cm}|p{0,5cm}|p{0,5cm}|p{0,5cm}|}
\caption{Questionnaire: user confidence}\label{table:test-results}\\
\hline
\textbf{Please answer how confident do you feel the following features work and meet your expectations on the scale of 1 (Not at all confident) to 5 (Very confident).} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5}\\
\hline
\endfirsthead
\multicolumn{6}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\textbf{Please answer how confident do you feel the following features work and meet your expectations on the scale of 1 (Not at all confident) to 5 (Very confident).} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} \\
\hline
\endhead
\hline \multicolumn{6}{c}{\textit{Continues on next page}} \\
\endfoot
\hline
\endlastfoot
I can import images from the lab’s OMERO server. & 0 & 0 & 0 & 0 & 3 \\ \hline
I can import images from my local computer. & 0 & 0 & 0 & 0 & 3 \\ \hline
My data is saved on the lab’s PostgreSQL server. & 0 & 0 & 0 & 0 & 3 \\ \hline
My data persist locally between work sessions. & 0 & 0 & 0 & 0 & 3 \\ \hline
I can add and modify measurement types. & 0 & 0 & 0 & 0 & 3 \\ \hline
I can add and modify gels. & 0 & 0 & 0 & 0 & 3 \\ \hline
I can add and modify the general information about the lanes on the gel. & 0 & 0 & 0 & 0 & 3 \\ \hline
I can add multiple images for gels. & 0 & 0 & 0 & 0 & 3 \\ \hline
I can view the raw image before analysis. & 0 & 0 & 0 & 0 & 3 \\ \hline
I can select and rotate a region on the image before analysis. & 0 & 0 & 0 & 0 & 3 \\ \hline
I can specify if the background on the image is dark or light. & 0 & 0 & 0 & 0 & 3 \\ \hline
I can correct image background. & 0 & 0 & 1 & 0 & 2 \\ \hline
I can choose a false-color mapping for the image. & 0 & 0 & 1 & 0 & 2 \\ \hline
I can mark the lane positions and widths on the gel image. & 0 & 0 & 0 & 1 & 2 \\ \hline
I can adjust lane widths individually. & 0 & 0 & 0 & 0 & 3 \\ \hline
I can see pixel intensity plots for marked lanes. & 0 & 0 & 0 & 1 & 2 \\ \hline
I can specify a zero-line to separate background from signal on the intensity plots. & 0 & 0 & 0 & 1 & 2 \\ \hline
I can add and modify measurements connected to specific gel images. & 0 & 0 & 0 & 0 & 3 \\ \hline
I can choose which lanes a measurement includes. & 0 & 0 & 1 & 0 & 2 \\ \hline
I can specify the integration limits on the pixel intensity plots. & 0 & 0 & 0 & 1 & 2 \\ \hline
I can see a comparison and annotate analyzed lanes for measurements. & 0 & 0 & 0 & 0 & 3 \\ \hline
I can undo an accidental modification. & 0 & 0 & 0 & 0 & 3 \\ \hline
I can disable all editing operations to avoid accidental modifications during a review. & 0 & 1 & 0 & 0 & 2 \\ \hline
I can change my image and data source parameters after initial setup. & 0 & 0 & 0 & 1 & 2 \\ \hline
I can use the software on macOS computer. & 1 & 0 & 2 & 0 & 0 \\ \hline
I can use the software on Windows computer. & 1 & 0 & 1 & 0 & 1 \\ \hline
I can use the software on Linux computer. & 0 & 0 & 0 & 0 & 3 \\
\end{longtable}
