\small

\begin{longtable}[h!]{|p{0.02\linewidth} | p{0.7\linewidth} | p{0.05\linewidth}| p{0.05\linewidth}|}
\caption{Requirements satisfied by alternative applications}\label{table:alternative-comparison-results}\\
\hline
\rot{\textbf{Requirement No.}} & \rot{\textbf{Requirement}} & \rot{\textbf{ImageJ}} & \rot{\textbf{Image Lab}}\\
\hline
\endfirsthead
\multicolumn{4}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\rot{\textbf{Requirement No.}} & \rot{\textbf{Requirement}} & \rot{\textbf{ImageJ}} & \rot{\textbf{Image Lab}}\\
\hline
\endhead
\multicolumn{4}{c}{\textit{Continues on next page}} \\
\endfoot
\hline
\endlastfoot
1 & I want the software to be released under GPLv3 license. & Yes & No\\ \hline
2 & I want GitLab pipeline configured to build packaged executables. & N/A & N/A\\ \hline
3 & I want the software to look as agreed on the UI design document. & N/A & N/A\\ \hline
4 & I want to import images from the lab’s OMERO server. & No & No\\ \hline
5 & I want my data saved on the lab’s PostgreSQL server. & No & No\\ \hline
6 & I want the software to indicate when it has lost external connections and allow to retry or change connection parameters. & N/A & N/A \\ \hline
7 & I want to import images from my local computer. & Yes & Yes\\ \hline
8 & I want my data to persist between work sessions locally. & No & No\\ \hline
9 & I want to export the results of my work as a CSV file. & Yes & Yes\\ \hline
10 & I want to use the software in my own language. & No & No\\ \hline
11 & I want to add and modify measurement types. & No & No\\ \hline
12 & I want to add and modify gels. & No & No\\ \hline
13 & I want to add and modify the general information about the lanes on the gel. & No & Yes\\ \hline
14 & I want to add multiple images for gels. & Yes & Yes\\ \hline
15 & I want to view the raw image before analysis. & Yes & Yes\\ \hline
16 & I want to select a ROI on the image before analysis (rotate and crop). & Yes & Yes\\ \hline
17 & I want to specify if the background on the image is dark or light. & Yes & Yes\\ \hline
18 & I want to correct image background (subtraction by rolling ball method). & Yes & Yes\\ \hline
19 & I want to choose a false-color mapping for the image. & Yes & Yes\\ \hline
20 & I want to mark the lane positions and widths on the gel image. & Yes & Yes\\ \hline
21 & I want to adjust lane widths individually. & No & Yes\\ \hline
22 & I want to rotate the lanes individually. & No & Yes\\ \hline
23 & I want to curve the lanes individually. & No & Yes\\ \hline
24 & I want to see pixel intensity plots for marked lanes. & Yes & Yes\\ \hline
25 & I want to specify a zero-line to separate background from signal on the intensity plots. & Yes & Yes\\ \hline
26 & I want to add and modify measurements connected to specific gel images. & N/A & N/A\\ \hline 
27 & I want to choose which lanes a measurement includes. & Yes & Yes\\ \hline
28 & I want to specify the integration limits on the pixel intensity plots. & Yes & Yes\\ \hline
29 & I want the selected limits to be visible on their lanes. & Yes & Yes\\ \hline
30 & I want to see a comparison and annotate analyzed lanes for measurements. & Yes & Yes\\ \hline
31 & I want to search previously analyzed gels by name, ID, sample ID, lane ID and measurement ID. & Yes & Yes\\ \hline
32 & I want the option to undo an accidental modification. & No & Yes\\ \hline
33 & I want a way to disable all editing operations to avoid accidental modifications during a review. & Yes & Yes\\ \hline
34 & I want to change my image and data source parameters after initial setup. & No & No\\ \hline
35 & I want to use the software on macOS computer. & Yes & Yes\\ \hline
36 & I want to use the software on Windows computer. & Yes & Yes\\ \hline
37 & I want to use the software on Linux computer. & Yes & No\\ \hline
38 & I want a user manual for the software. & Yes & Yes\\ \hline
39 & I want the implementation of analysis steps formally documented. & Yes & Yes\\
\end{longtable}
